Brother, Can You Spare a Manufacturing Job?  How Voters React to Deindustrialization

### 2021-12-10 Final Draft/Final Draft.Rmd
typo fix

While our study is oriented towards history, deindustrialization is in no way confined to the past. The trajectory of American manufacturing employment is far from certain, with continued competition from abroad and the perennial threat of unemployment. We believe the case of the U.S. also offers insight that is applicable to the phenomenon of 'premature deindustrialization' in the developing world, and the concurrent growth of populist parties in Hungary, Brazil, India and elsewhere. XXXXXXXXXXXXXXX CITE XXXXXXxx

>>>>

While our study is oriented towards history, deindustrialization is in no way confined to the past. The trajectory of American manufacturing employment is far from certain, with continued competition from abroad and the perennial threat of automation. We believe the case of the U.S. also offers insight that is applicable to the phenomenon of 'premature deindustrialization' in the developing world, and the concurrent growth of populist parties in Hungary, Brazil, India and elsewhere. XXXXXXXXXXXXXXX CITES XXXXXXxx
